### 2017-08-27 README.Rmd
builds after rr, vignette, readme tweaks

The statistical methodology implemented computes targeted minimum loss-based
estimates of well-studied variable importance measures:

1. The _average treatment effect_ (ATE) for discrete exposures/treatments,
2. A _nonparametric variable importance measure_ (NPVI) for continuous exposures
[@chambaz2012estimation].

@@

1. Pre-screening of genomic sites is used to isolate a subset of sites for
which there is cursory evidence of differential methylation. For the sake of
computational feasibility, targeted minimum loss-based estimates of VIMs are
computed only for this subset of sites. Several screening approaches are
available, adapting core routines from the following R packages:
[`limma`](http://bioconductor.org/packages/release/bioc/html/limma.html),
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi).
2. Nonparametric VIMs are estimated for the specified parameter, currently using
routines from the R packages
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi) (to estimate the
NPVI parameter) or [`tmle`](https://CRAN.R-project.org/package=tmle) (to
estimate the ATE).
3. Since pre-screening is performed prior to estimating VIMs, we make use of a
multiple testing correction uniquely suited to such settings. Due to the
multiple testing nature of the estimation problem, a variant of the Benjamini &
Hochberg procedure for controlling the False Discovery Rate (FDR) is applied
[@benjamini1995controlling]. Specifically, we apply the modified marginal
Benjamini & Hochberg step-up False Discovery Rate controlling procedure for
multi-stage analyses (FDR-MSA) [@tuglus2009modified].

@@

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.

>>>>

The statistical methodology implemented computes targeted minimum loss-based
estimates of several well-characterized variable importance measures:

For discrete-valued treatments or exposures:
* The _average treatment effect_ (ATE):
  $$ \Psi_{ATE} = E[E[Y_j \mid A = 1, W_{-j}] - E[Y_j \mid A = 0, W_{-j}]],$$
  where $j$ indexes a target CpG site of interest and $-j$ gives all CpG sites
  in the same neighborhood as the target site except the target site itself
  (i.e., the neighboring sites).

* The _relative risk_ (RR), where
  $$ \dots,$$
  where...

For continous-valued treatments or exposures:
* A _nonparametric variable importance measure_ (NPVI) [@chambaz2012estimation].

@@

1. Pre-screening of genomic sites is used to isolate a subset of sites for
which there is cursory evidence of differential methylation. For the sake of
computational feasibility, targeted minimum loss-based estimates of VIMs are
computed only for this subset of sites. Several screening approaches are
available, adapting core routines from the following R packages:
[`limma`](http://bioconductor.org/packages/release/bioc/html/limma.html),
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi).
2. Nonparametric VIMs are estimated for the specified parameter, currently
adapting routines from the
[`tmle.npvi`](https://CRAN.R-project.org/package=tmle.npvi) and
[`tmle`](https://CRAN.R-project.org/package=tmle) R packages.
3. Since pre-screening is performed prior to estimating VIMs, we make use of a
multiple testing correction uniquely suited to such settings. Due to the
multiple testing nature of the estimation problem, a variant of the Benjamini &
Hochberg procedure for controlling the False Discovery Rate (FDR) is applied
[@benjamini1995controlling]. Specifically, we apply the modified marginal
Benjamini & Hochberg step-up False Discovery Rate controlling procedure for
multi-stage analyses (FDR-MSA) [@tuglus2009modified].

@@

<!--
Note about shrinkage of influence curves, adapting @smyth2004linear.
Specifically, this is meant to reference my working paper with Alan.
